\begin{enumerate}
\item
  Write a C/C++ POSIX compliant program to check the following limits:
  \begin{enumerate}
	\item No. of clock ticks
	\item Max. no. of child processes
	\item Max. path length
	\item Max. no. of characters in a file name
	\item Max. no. of open files/ process
  \end{enumerate}
\item
  Write a C/C++ POSIX compliant program that prints the POSIX defined
  configuration options supported on any given system using feature test
  macros.
\item
  Consider the last 100 bytes as a region. Write a C/C++ program to
  check whether the region is locked or not. If the region is locked,
  print pid of the process which has locked. If the region is not
  locked, lock the region with an exclusive lock, read the last 50 bytes
  and unlock the region.
\item
  Write a C/C++ program which demonstrates interprocess communication
  between a reader process and a writer process. Use mkfifo, open, read,
  write and close APIs in your program.
\item
  Write a C/C++ program that outputs the contents of its Environment
  list.
\item
  Write a C / C++ program to emulate the unix ln command
\item
  Write a C/C++ program to illustrate the race condition.
\item
  Write a C/C++ program that creates a zombie and then calls system to
  execute the ps command to verify that the process is zombie.
\item
  Write a C/C++ program to avoid zombie process by forking twice.
\item
  Write a C/C++ program to implement the system function.
\item
  Write a C/C++ program to set up a real-time clock interval timer using
  the alarm API.
\item
  Write a C program to implement the syntax-directed definition of ``if
  E then S1'' and ``if E then S1 else S2''. (Refer Fig. 8.23 in the text
  book prescribed for 06CS62 Compiler Design, Alfred V Aho, Ravi Sethi,
  and Jeffrey D Ullman: Compilers- Principles, Techniques and Tools, 2nd
  Edition, Pearson Education, 2007).
\item
  Write a yacc program that accepts a regular expression as input and
  produce its parse tree as output.
\end{enumerate}
